Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-05-30 graviton spectra/content/br.tex
merge

In \cite{RSW,RWindex} we describe how physical fields in supergravity are manifest in the twisted model.
We review a small part of this.
If $\til{Z}$ is an eleven-manifold equipped with a THF structure as above, the fields will live in a space of the form
\beqn
\cA^\bu(\til{Z}, \til{V})
\eeqn
where
\begin{itemize}
\item The graded bundle $\til{V}$ is holomorphic with respect to the THF structure.
\item $\cA^\bu (\til{Z}, \til{V})$ denotes the THF cohomology of $\til{Z}$ with coefficients in $\til{V}$.
\end{itemize}
To simplify discussion in the remainder of this section we will only work in the local model~\eqref{eqn:local} where $\til{Z} = \R \times Z$ for $Z$ a Calabi--Yau fivefold.
Then, the space of fields is of the form
\beqn
\Omega^\bu(\R) \otimes \Omega^{0,\bu}(Z, V)
\eeqn
where $V$ is some holomorphic vector bundle on $Z$.\footnote{The tensor product $\otimes$ is the completed tensor product with respect to natural topologies present in the space of sections of a smooth vector bundle.}
Since the theory is of topological/holomorphic nature, there is a linear part of the BRST differential of the form $\d + \dbar$ where $\d$ is the de Rham differential on $\R$ and $\dbar$ corresponds to the holomorphic structure on the bundle $V$.

@@

\begin{conj}\label{conj:ads7}
The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E_{AdS_7}$. 
\end{conj}

>>>>

In \cite{RSW,RWindex} we describe how physical fields in supergravity are manifest in the twisted model.
We review a small part of this.
If $\til{Z}$ is an eleven-manifold equipped with a THF structure as above, the fields will live in a space of the form
\beqn
\cA^\bu(\til{Z}, \til{V})
\eeqn
where
\begin{itemize}
\item The graded bundle $\til{V}$ is holomorphic with respect to the THF structure.
\item $\cA^\bu (\til{Z}, \til{V})$ denotes the THF cohomology of $\til{Z}$ with coefficients in $\til{V}$. \brian{elaborate}
\end{itemize}
To simplify discussion in the remainder of this section we will only work in the local model~\eqref{eqn:local} where $\til{Z} = \R \times Z$ for $Z$ a Calabi--Yau fivefold.
Then, the space of fields is of the form
\beqn
\Omega^\bu(\R) \otimes \Omega^{0,\bu}(Z, V)
\eeqn
where $V$ is some holomorphic vector bundle on $Z$.\footnote{The tensor product $\otimes$ is the completed tensor product with respect to natural topologies present in the space of sections of a smooth vector bundle.}
Since the theory is of topological/holomorphic nature, there is a linear part of the BRST differential of the form $\d + \dbar$ where $\d$ is the de Rham differential on $\R$ and $\dbar$ corresponds to the holomorphic structure on the bundle $V$.

@@

\begin{conj}\label{conj:ads7}
The minimal twist of eleven-dimensional supergravity on the $AdS_7\times S^4$ background with $N$ units of M5 brane flux supported on $S^4$ is perturbatively equivalent to $\mc E^N_{AdS_7}$. 
\end{conj}

### 2023-05-30 graviton spectra/content/e16.tex
merge

This result induces a product decomposition 
\[
 \cA_M^\bu(\mc L^{r=0}_{AdS_4} ) = \prod _{n\geq -2} \mc F^{(n)}_{M}
\]
\brian{gradings again}
where $\cF^{(n)}_M \subset \cA_M^\bu(\mc L^{r=0}_{AdS_4} )$ is the weight $n$ eigenspace with respect to the above $\C^\times$ action thought of as a complex of super vector bundles on $M$. 
In particular, we see that $\mc F^{(0)}_{M}$ is itself a local dg Lie algebra, for which  every $\mc F^{(n)}_{M}$ is a module.

@@

\begin{lem}
There is an isomorphism of elliptic complexes 
\[ \mc F^{(-1)}_{M} \cong \cA^\bu_M \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
\end{lem}
\begin{proof}
The sections of this specified weight are:
\begin{itemize}
\item sections of type $\mu$ of the form $\mu_a(z) \del_{w_a}$. 
As the $w_a$ are fiber coordinates on $K^{1/4}$, these fields transform as sections of $K^{1/4}_\C$.
\item sections of type $\gamma$ of the form $\gamma_a(z) \d w_a$. 
These fields transform as sections of $K^{3/4}$. 
\end{itemize}
\end{proof}

>>>>

This result induces a product decomposition 
\[
 \cA_M^\bu(\mc L^{r=0}_{AdS_4} ) = \prod _{n\geq -2} \mc F^{(n)}_{M}
\]
where $\cF^{(n)}_M \subset \cA_M^\bu(\mc L^{r=0}_{AdS_4} )$ is the weight $n$ eigenspace with respect to the above $\C^\times$ action thought of as a complex of super vector bundles on $M$. 
In particular, we see that $\mc F^{(0)}_{M}$ is itself a local dg Lie algebra, for which  every $\mc F^{(n)}_{M}$ is a module.

@@

\begin{lem}
There is an isomorphism of elliptic complexes 
\[ \mc F^{(-1)}_{M} \cong \cA^\bu_M \left (K^{1/4}\otimes (\C^4)^* \oplus \Pi K^{3/4}\otimes \C^4 \right ) \]
\end{lem}
\begin{proof}
The sections of this specified weight are:
\begin{itemize}
\item sections of type $\mu$ of the form $\mu_a(z) \del_{w_a}$. 
As the $w_a$ are fiber coordinates on $K^{1/4}$, these fields transform as sections of $K^{1/4}$.
\item sections of type $\gamma$ of the form $\gamma_a(z) \d w_a$. 
These fields transform as sections of $K^{3/4}$. 
\end{itemize}
\end{proof}

### 2023-05-30 graviton spectra/content/index.tex
merge

Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
\beqn\label{eqn:cotm2}
\cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right) 
\eeqn
For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

@@

 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
       \ul{+} & \ul{-} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
\\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O \end{tikzcd}
\end{equation}

We denote by $\cF_{AdS_4}$ the factorization algebra on $M = \R\times \C$ which assigns to an open set $U \subset \R \times \C$ the cochain complex
\beqn
 \cF_{AdS_4} (U) = \cO\left(\cA^\bu(U,\mc L^N_{AdS_4}) \right ) .
\eeqn
%Here, $\cA^\bu(U, \cL^N_{AdS_4}$

@@

\begin{defn}\label{defn:ads4states}
The \emph{space of supergravity states} $\cS_{AdS_4}$ on twisted $AdS_4\times S^7$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_4}$:
\beqn
\cS_{AdS_4} \define \cF_{AdS_4} (0) .
\eeqn
\end{defn}

@@

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra 
\beqn
\cS_{AdS_4} = \Sym (\mc H_{AdS_4})
\eeqn
where $\mc H_{AdS_4}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

\begin{proof}
To characterize the costalk at $0 \in \R \times \C$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence. Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc. The sections of the sheaf of cochain complexes $\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}(D)\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O(D) \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}(D)\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Gamma (D, \Omega^1) \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O(D)
\end{tikzcd}
\end{equation}

@@

We denote by $\cF_{AdS_7}$ the factorization algebra on $X = \C^3$ which assigns to an open set $U \subset \C^3$ the cochain complex
\beqn
 \cF_{AdS_7} (U) = \cO\left(\Omega^{0,\bu}(U,\mc L^N_{AdS_7}) \right ) .
\eeqn
\brian{what's the dependence on $N$?}
%Here, $\cA^\bu(U, \cL^N_{AdS_4}$

\begin{defn}\label{defn:ads7states}
The \emph{space of supergravity states} $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_7}$:
\beqn
\cS_{AdS_7} \define \cF_{AdS_7} (0) .
\eeqn
\end{defn}

@@

\begin{lem}
The space of supergravity states $\cS_{AdS_7}$ on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex

@@

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $M$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{0}_{AdS_4})|_{\{\infty\} \times M}$ is given by the complex of bundles $\cA^\bu_{M}(\mc L_{AdS_4}^{r=0})$ on $M$.

\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $X$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{+} & \ul{-} \\
\C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
\C[w_1, w_2]   \otimes \T\ar[ur, "\del^X_\Omega" description] \\
\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{0}_{AdS_7})|_{\{\infty\} \times X}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
\end{itemize}

These Lagrangians exist in the fully interacting eleven-dimensional model, which we can encode perturbatively in terms of an $L_\infty$ structure.
In particular, the parity shift of these Lagrangians are equipped with $L_\infty$ structures compatible with the interacting bulk theory in the sense that the morphisms
\begin{align*}
\cA_M^\bu (\mc L^{r=0}_{AdS_4} ) & \to (p_* \mc E^0 _{AdS_4})|_{\{\infty\} \times M}\\
\Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) & \to (p_* \mc E^0 _{AdS_7})|_{\{\infty\} \times X}
\end{align*}
preserve the $L_\infty$ brackets even taking into account the potential for additional higher brackets on the target coming from homotopy transfer. 
%Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$

@@

\brian{I think gradings need to be fixed.}

\brian{The dependence on $N$ on the RHS is implicit in above definitions. Explain we are setting $N=0$.}

>>>>

Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
\beqn\label{eqn:cotm2}
\cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \cA_M^\bu \ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \cA_M^\bu  \\
\C[w_1,\ldots, w_4] \otimes \cA_M^\bu (\T) \ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \cA_M^\bu \ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \cA_M^\bu(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \cA_M^\bu  \end{tikzcd} \right) 
\eeqn
For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

@@

 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
       \ul{+} & \ul{-} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
\\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O \end{tikzcd}
\end{equation}

We denote by $\Obs_{AdS_4}$ the factorization algebra on $M = \R\times \C$ which assigns to an open set $U \subset \R \times \C$ the cochain complex
\beqn
 \Obs^N_{AdS_4} (U) = \cO\left(\cA^\bu(U,\mc L^N_{AdS_4}) \right ) .
\eeqn
%Here, $\cA^\bu(U, \cL^N_{AdS_4}$

@@

\begin{defn}\label{defn:ads4states}
The \emph{space of supergravity states} $\cS^N_{AdS_4}$ on twisted $AdS_4\times S^7$ is given by the cochain complex given by the costalk at zero of $\Obs_{AdS_4}^N$:
\beqn
\cS^N_{AdS_4} \define \Obs^N_{AdS_4} (0) .
\eeqn
\end{defn}

@@

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra 
\beqn
\cS^N_{AdS_4} = \Sym (\mc H_{AdS_4})
\eeqn
where $\mc H_{AdS_4}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

\begin{proof}
To characterize the costalk at $0 \in \R \times \C$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence. Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc. The sections of the sheaf of cochain complexes $\cA^\bu_{\R \times \C}(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}(D)\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O(D) \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}(D)\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Gamma (D, \Omega^1) \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O(D)
\end{tikzcd}
\end{equation}

@@

We denote by $\Obs_{AdS_7}$ the factorization algebra on $X = \C^3$ which assigns to an open set $U \subset \C^3$ the cochain complex
\beqn
 \Obs_{AdS_7}^N (U) = \cO\left(\Omega^{0,\bu}(U,\mc L^N_{AdS_7}) \right ) .
\eeqn
\brian{what's the dependence on $N$?}
%Here, $\cA^\bu(U, \cL^N_{AdS_4}$

\begin{defn}\label{defn:ads7states}
The \emph{space of supergravity states} $\cS^N_{AdS_7}$ on twisted $AdS_7\times S^4$ is given by the cochain complex given by the costalk at zero of the factorization algebra $\cF_{AdS_7}$:
\beqn
\cS_{AdS_7}^N \define \cF_{AdS_7} (0) .
\eeqn
\end{defn}

@@

\begin{lem}
The space of supergravity states $\cS_{AdS_7}^N$ on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex

@@

Explicitly these Lagrangians in the phase space are described as follows.
\begin{itemize}
\item Let $\mc L_{AdS_4}^{r=0}$ denote the following complex of vector bundles on $M$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,\ldots, w_4]  \otimes \mc O \\
\C[w_1,\ldots, w_4]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4]\otimes \Omega^1 \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{N=0}_{AdS_4})|_{\{\infty\} \times M}$ is given by the complex of bundles $\cA^\bu_{M}(\mc L_{AdS_4}^{r=0})$ on $M$.

\item Let $\mc L_{AdS_7}^{r=0}$ denote the following complex of vector bundles on $X$
 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
   \ul{-} & \ul{+} \\
\C[w_1, w_2] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] &\C[w_1,w_2]  \otimes \mc O \\
\C[w_1, w_2]   \otimes \T\ar[ur, "\del^X_\Omega" description] \\
\C[w_1, w_2] \otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & \C[w_1,w_2]\otimes \Omega^1 \\ & \C[w_1, w_2] \{\d w_a\}  \otimes \mc O
\end{tikzcd}
\end{equation}
The desired Lagrangian in $(p_*\mc E^{N=0}_{AdS_7})|_{\{\infty\} \times X}$ is given by $\Omega^{0,\bullet}_{X} (\mc L_{AdS_7}^{r=0})$.
\end{itemize}

These Lagrangians exist in the fully interacting eleven-dimensional model, which we can encode perturbatively in terms of an $L_\infty$ structure.
In particular, the parity shift of these Lagrangians are equipped with $L_\infty$ structures compatible with the interacting bulk theory in the sense that the morphisms
\begin{align*}
\cA_M^\bu (\mc L^{r=0}_{AdS_4} ) & \to (p_* \mc E^{N=0} _{AdS_4})|_{\{\infty\} \times M}\\
\Omega^{0,\bullet}_{X} (\mc L^{r=0}_{AdS_7} ) & \to (p_* \mc E^{N=0} _{AdS_7})|_{\{\infty\} \times X}
\end{align*}
preserve the $L_\infty$ brackets even taking into account the potential for additional higher brackets on the target coming from homotopy transfer. 
%Indeed, such brackets must necessarily involve classes in $H^2_{\mr{THF}} \left ( (\R\times \C^2)\setminus 0 \right )$

@@
